Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 18:10

The use of the actual modeled values of clear sky GHI, described above , can not provide us with
a robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs, 
so we created an upper envelope of the clear sky irradiance,

.............................

above which, any GHI value can safely attributed to CE.  We evaluated the performance
of the modeled clear radiation for each of atmospheric level of clearness, as
reference, in order to conclude which is the most appropriate.

>>>>

The use of the actual modelled values of clear sky GHI, described above, can not
provide us with a robust method to distinguish the CE cases, due to the limited
accuracy of the input data, and the natural variability of the atmosphere. Our main
focus was to positively identify over irradiance events related to CEs.  For this
reason, we created an upper envelope of the clear sky irradiance, above which, any
GHI value can safely be attributed to CE a event.

We had to select both, an appropriate set of atmospheric parameterization, in
Libradtran, and the thresholds of CE identification.
First we evaluated the performance of the modelled clear radiation, for each of
atmospheric level of clearness we have created as reference, in order to conclude
which is the most appropriate.
